Paper Nine Summary

### 2015-12-12 hw/read/9/summary.tex
fixed typos

\section*{Possible Improvements}
\begin{itemize}
\item The authors make a statement on page five in the section on expirimental design that is unfortunately false.  They state that 10-fold cross validation essetially uses 90 percent of the training data and 10 percent of the test data as a downside of 10-fold cross validation.  They neglect to state that it does that 10 times and actually goes through the entireity of the 10 possible permutations of the data and calculates its error based on that.  It may have been enough to state that random split was used widely in the literature and leave out the statement on 10-fold.

>>>>

\section*{Possible Improvements}
\begin{itemize}
\item The authors make a statement on page five in the section on experimental design that is unfortunately false.  They state that 10-fold cross validation essentially uses 90 percent of the training data and 10 percent of the test data as a downside of 10-fold cross validation.  They neglect to state that it does that 10 times and actually goes through the entirety of the 10 possible permutations of the data and calculates its error based on that.  It may have been enough to state that random split was used widely in the literature and leave out the statement on 10-fold.
